\LARGE \bf DexNet 1.0: Correlated Multi-Armed Bandit Models for Large Scale 3D Grasp Planning Under Uncertainty \versionline{2}

### 2015-08-26 ICRA2016/bandits_docs/includes/background.tex
Created new figures and updated the full draft. Things are pretty rough but starting to come together. Still need to add new experiments, add a full algorithm section, clarify the use of priors, fill out neural net discussion, and generally clean thigns up. We are already beyond the acceptable length.

\section{Continuous Correlated Beta Processes}
\seclabel{background}

We use Continuous Correlated Beta Processes (CCBPs) to model correlations in the probability of force closure between two grasps.
For example, two grasps that contact the shape in similar locations may have similar probabilities of force closure.
We refer the reader to Goetschalckx et al.~\cite{} for a detaled description of CCBPs.

\subsection{Beta-Bernoulli Processes}

Consider a set of $K$ grasps $\Gamma = \{g_k\}_{k=1}^K$.
Then force closure for each grasp $F(g_k) \in \{0, 1\}$ is a Bernoulli random variable with probability of success $\theta_k = P_F(g_k)$.
Since we do not know the value of $\theta_k$ for each grasp, we can specify a distribution of $\theta_k$ based on our prior belief about the likelihood of force closure.
A common choice for a prior on the Bernoulli parameter $\theta_k$ is the Beta distribution, which is specified by shape parameters $\alpha > 0$ and $\beta > 0$:

@@

\noindent This combination of indepdent Bernoulli random variables with Beta priors is known as a {\it Beta-Bernoulli process}.

Let our prior distribution on $\theta_k$ be a beta distribution with parameters $\alpha_{k,0}$, $\beta_{k,0}$.
Then after observing force closure for $t$ samples $F_{1}(g_k), ..., F_{t}(g_k)$ from our uncertainty model, our posterior distribution on the Bernoulli success probability $\theta_k$ is obtained using Bayes rule.
This yields~\cite{laskey2015bandits}

\vspace{-2ex}
\begin{align*}
	p \left(\theta_k | F_{1}(g_k), ..., F_{t}(g_k) \right) &= \betadist\left( \alpha_{k,t}, \beta_{k,t} \right) \\
	\alpha_{k,t} &= \alpha_{k,0} + \sum \limits_{i=1}^t F_{i}(g_k) \\
	\beta_{k,t} &= \beta_{k,0} + \sum \limits_{i=1}^t (1 - F_{i}(g_k))
\end{align*}

\noindent Therefore the belief distribution on the probability of force closure $\theta_k$ can be updated by incrementing the value of $\alpha$ and $\beta$ for each force closure observed.
The expected value of $\theta_k$ after the observations is

\begin{align*}
	\mathbb{E} \left[ \theta_k | F_{1}(g_k), ..., F_{t}(g_k) \right] = \frac{\alpha_{k,t}}{\alpha_{k,t} + \beta_{k,t}} = \frac{\mbox{\#Successes} +	
	\alpha_{k,0}}{\mbox{\#Trials}+\alpha_{k,0}+\beta_{k,0}}.
\end{align*}

Continuous Correlated Beta Processes(CCBPs) were introduced by Goetschalckx et al.~\cite{} to model correlations between the Bernoulli random variables in a Beta-Bernoulli process, which may lead to faster convergence in Multi-Armed Bandit problems~\cite{}.
Such correlations may exist when the Bernoulli random variables depend on common latent factors.
For example, two probability of force closure variables $\theta_k$ may be correlated when two grasps have similar poses or when the surface geometry near the points at which they contact an object are similar.

A CCBP is a Beta-Bernoulli process with an additional parameter $k(g_i, g_j) : \mathcal{G} \times \mathcal{G} \rightarrow [0,1]$, called the kernel, that measures similarity between two grasps.
The kernel should approach 1 as the arguments become increasingly similar and approach 0 as the arguments become dissimilar.
Let $F_{1}(g_{I(1)}), ..., F_{t}(g_{I(t)})$ be $t$ observations of force closure from samples of our uncertainty models for grasps $g_{I(1)}, ..., g_{I(t)}$, where $I(j)$ is the index of the grasp sampled at time $j$.
Then the CCBP posterior update for $\theta_k$ is~\cite{}:

\vspace{-2ex}
\begin{align*}
	p \left(\theta_k | F_{1}(g_{I(1)}), ..., F_{t}(g_{I(t)}) \right) &= \betadist\left( \alpha_{k,t}, \beta_{k,t} \right) \\
	\alpha_{k,t} &= \alpha_{k,0} + \sum \limits_{j=1}^t k(g_k, g_{I(j)}) F_{i}(g_{I(j)}) \\
	\beta_{k,t} &= \beta_{k,0} + \sum \limits_{=1}^t k(g_k, g_{I(j)}) (1 - F_{i}(g_{I(j)}))
\end{align*}

\noindent Therefore grasps can constitute "effective" observations of other grasps if the two grasps are similar according to the kernel function.

>>>>

\section{Correlated Multi-Armed Bandit Model}
\seclabel{background}

Finding an approximate solution of Equation~\ref{eq:objective} using Multi-Armed Bandits requires a predictive model of the probability of force closure for each grasp.
We use Continuous Correlated Beta Processes (CCBPs) to model force closure for a grasp as a Bernoulli random variable with correlations across grasps and objects~\cite{goetschalckx2011continuous, montesano2012active}.
\figref{correlated-motivation} illustrates how using a correlated model can lead to accelerated convergence of bandit algorithms.
%In practice, correlations may occur between two grasps that contact the same shape in similar locations, or between grasps on different shapes, such as grasping the handle of a mug and the handle of a teapot.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.22]{figures/illustrations/correlated_bandits.png}
\caption{(Top Left) Consider a set of grasps with fixed center at an object center of mass and approach direction sampled along a one-dimensional circle. (Top Right) The true probability of force closure $P_F$ may vary smoothly as a function of the angle of the grasp axis. (Middle Left) Uncorrelated MAB models maintain an estimate of $P_F$ independently for each grasp, indicated by bars and their height. On iteration $T$ of a MAB algorithm, the grasp indicated with a green bar is sampled and returns force closure. (Middle Right) Only the estimate of $P_F$ for the sampled grasp is updated for iteration $T+1$, and the grasp with highest estimated $P_F$ remains suboptimal. (Bottom Left) Correlated MAB models maintain a global predictive function (in red) of $P_F$ for any possible grasp but may select grasps from a set of discrete candidates (indicated by dots). (Bottom Right) On iteration $T+1$ the grasp indicated by the green dot again returns force closure and the global model is updated, increasing the estimated $P_F$ for ``nearby" grasps. Although a suboptimal grasp was sampled, the global model now correctly predicts the optimal grasp in the set. }
\figlabel{correlated-model}
\vspace*{-15pt}
\end{figure}

Continuous Correlated Beta Processes(CCBPs) were independently developed by Goetschalckx et al.~\cite{goetschalckx2011continuous} and Montesano and Lopes~\cite{montesano2012active} to model correlations between the Bernoulli random variables in a Beta-Bernoulli process, which may lead to faster convergence in Multi-Armed Bandit problems~\cite{chu2011contextual}.
Such correlations may exist when the Bernoulli random variables depend on common latent factors.
For example, two probability of force closure variables $\theta_k$ may be correlated when two grasps contact the same shape in similar locations or when grasps on different shapes have similar local surface geometries, such as grasping the handle of a mug and the handle of a teapot

Let $\Gamma = \{\bg_k\}_{k=1}^K$ denote our discrete set of $K$ candidate grasps for object $\mO$.
Let $F(\bg_k) \in \{0, 1\}$ denote the occurence of force closure for a grasp $\bg_k$.
We model $F(\bg_k)$ as a Bernoulli random variable with probability of success $\theta_k = P_F(\bg_k)$.
Since we do not know the value of $\theta_k$ for each grasp, we maintain a belief distribution for each $\theta_k$ based on our prior belief about the likelihood of force closure.
A common choice for a belief distribution on the Bernoulli parameter $\theta_k$ is the Beta distribution, which is specified by shape parameters $\alpha > 0$ and $\beta > 0$:

@@

A CCBP estimates the shape parameters for a grasp $\bg$ on object $\mO$ using a normalized kernel function $k(\by_i, \by_j) : \mM \times \mM \rightarrow [0,1]$ that measures similarity between two elements of the Grasp Moduli Space, where $\by = \{\bg, \mO\} \in \mM$.
The kernel approaches 1 as the arguments become increasingly similar and approaches 0 as the arguments become dissimilar.
In this work we use a unit-bandwidth squared exponential kernel 
\begin{align*}
	k(\by_i, \by_j) &= \exp\left( - \frac{1}{2} \sum \limits_{m=1}^{N_f} w_m^2 \|\phi_m(\by_i) - \phi_m(\by_j)\|_2^2 \right)
\end{align*}
\noindent where $\phi_m: \mM \rightarrow \mathbb{R}^{d_m}$ for $m = 1, ..., N_f$ are feature mappings for a grasp and object to a $d_m$-dimensional Euclidean space and $w_m \in \mathbb{R}$ are weights scaling the relative contribution of the feature maps to the similarity metric.

Upon observing force closure for a grasp and object, we update the Beta belief for every other grasp proportional to how similar it is to the observed grasp as measured by the kernel. 
Let $F_{1}(\bg_{I(1)}), ..., F_{t}(\bg_{I(t)})$ be $t$ sequential observations of force closure from samples of our uncertainty models for grasps $\bg_{I(1)}, ..., \bg_{I(t)}$, where $I(j)$ is the index of the grasp sampled at time $j$.
Then the CCBP posterior update for $\theta_k$ is~\cite{goetschalckx2011continuous}:

\vspace{-2ex}
\begin{align}
	p \left(\theta_k | F_{1}(\bg_{I(1)}), ..., F_{t}(\bg_{I(t)}) \right) &= \betadist\left( \alpha_{k,t}, \beta_{k,t} \right) \notag \\
	\alpha_{k,t} = \alpha_{k,0} &+ \sum \limits_{j=1}^t k(\by_k, \by_{I(j)}) F_{i}(\bg_{I(j)}) \label{eq:alpha} \\
	\beta_{k,t} = \beta_{k,0} &+ \sum \limits_{=1}^t k(g\by_k, \by_{I(j)}) (1 - F_{i}(\bg_{I(j)})) \label{eq:beta}
\end{align}

\noindent Intuitively, this allows observations of one grasp to constitute fractional observations of similar grasps.

\subsection{Feature Mappings}
We use feature mappings $\phi_1, ..., \phi_{N_f}$ that capture both lsimilarity based on local surface geometry and grasp parameters and global object shape.

\subsubsection{Local Features}
Since grasps may be correlated across very small changes to the grasp center and approach direction on a single shape, our first feature map $\phi_{\ell}(\by) = \bg$ is the identity transformation for the grasp.
However, similarity between grasp centers and approach directions does not indicate similar $P_F$ if the two surfaces are dissimilar.
For example, two grasps contacting a box on opposite sides of a corner may be very similar according to $\phi_{\ell}$ but likely to contact the object on surfaces with very different orientations.

To mitigate this issue, we use a variant of the grasp heightmap features of Herzog et al.~\cite{herzog2012template} and Kappler et al.~\cite{kappler2015leveraging}.
In this work, we capture local surface patches by an image oriented along a tangent plane to the grasp axis at a contact point, where each pixel stores the distance from the pixel center on the plane to the surface along the grasp axis.
Let $d_g \in \mathbb{Z}$ be the number of pixels along each dimension of the heightmap, let $\delta \in \mathbb{R}$ be the resolution of the image pixels in meters, and let $r \in \mathbb{R}$ be a minimum projection distance.
Furthermore, let $\bc_k, k = 1, 2$ be a contact point for grasp $\bg$ and let $\bt_1, \bt_2$ be two orthogonal vectors to the grasp approach direction $\bv$.
Then to compute the heightmap value at pixel $(i,j)$ we first compute the 3D location of the pixel on the plane, $\bp_k(i,j) = \bc_k + i \delta \bt_1 + j \delta \bt_2$.
Then we assign the heightmap value $\bh_k(i,j) = t^*$, where $t^*$ is the smallest value of $t > -r$ such that $\bp_k(i,j) + t \bv$ contacts the shape surface.
Finally, we rotate the heightmap to align the axes with the eigenvectors of a weighted covariance matrix as in~\cite{tombariunique} in order to make our feature representation rotationally invariant.
Our feature vector for the heightmaps is $\phi_{h}(\bg_i, \mO_i) = [\bh_1, \bh_2]^T$.
\figref{local-feature-model} illustrates local surface patches extracted by this procedure.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.35]{figures/illustrations/local_feature_model.png}
\caption{Three local surface heightmaps extracted on a teapot. Each heightmap is ``rendered" along the grasp axis at each contact point and oriented by the local directions of maximum variation in the heightmap.  }
\figlabel{local-feature-model}
\vspace*{-15pt}
\end{figure}

\subsubsection{Global Features}
Purely local features may not capture all correlations in probability of force closure between pairs of grasps and objects.
For example, grasps on the handle of a teapot may have similar grasp center, grasp axis, and even local surface geometry to another tubelike object such as a pen, but different $P_F$.
To measure global shape similarity, we develop a novel viewpoint-based object representation that pools the views from many virtual viewpoints rendered on a sphere surrounding the object.

\TODO{Justify why class labels help, if they do}
\figref{global-feature-model} illustrates our method.
We first render every object to 50 virtual cameras discretized along equal angle increments and oriented toward the object center using Maya.
Then we finetune AlexNet~\cite{krizhevsky2012imagenet}, a common deep Convolutional Neural Network (CNN) architecture, to predict a class label for each image based on known class labels for the 3D models.
%While class labels are not necessarily indicative of similarity in the geometry relevant to grasping, in many cases the same class label is enough to guarantee some correspondence of global geometry.
Next, we pass each of the 50 views of each object through the finetuned CNN and max-pool the output of the fc7 layer.
As the output is nearly 400 dimensions, we finally reduce the max-pooled output to 100 dimensions using Principal Component Analysis (PCA).
This yields a representation $\psi(\mO) \in \mathbb{R}^{100}$ for each object.

\TODO{Expand above paragraph, include more details on method as well as the results of training}

\begin{figure}[t!]
\centering
\includegraphics[scale=0.3]{figures/illustrations/cnn_model.png}
\caption{Illustration of our method for embedding 3D object models in a Euclidean vector space for computing global shape similiarty. We pass a set of 50 virtually rendered camera viewpoints discretized around a sphere through a deep Convolutional Neural Network (CNN) with the AlexNet~\cite{krizhevsky2012imagenet} architecture. Finally, we take the maximum fc7 response across each of the 50 views for each dimension and run PCA to reduce the dimensionality of the output.}
\figlabel{global-feature-model}
\vspace*{-15pt}
\end{figure}

\subsection{Optimizing Feature Weights}
One remaining issue is the selection of the relative feature weights $w_1, ..., w_{N_f}$.
Past work has optimized these weights using a squared error loss on the probability of success predicted by the CCBP and a true probability of success from brute force evaluation~\cite{montesano2012active}.
However, this criterion may be inappropriate for predicting probabilities, as the predictions must be bounded between 0 and 1.
In this work we instead select the weights which minimze the cross entropy loss~\cite{}:

\begin{align*}
	w_1^*, ..., w_{N_f}^* = \myargmin{w_1 \geq 0, ..., w_{N_f} \geq 0} \frac{1}{M} \sum \limits_{i=1}^M &\mu_i \log \left( \frac{\alpha_i}{\alpha_i + \beta_i} \right) + \\  &(1 - \mu_i) \log \left( \frac{\beta_i}{\alpha_i + \beta_i} \right)
\end{align*}
\noindent where $\alpha_i$ and $\beta_i$ are the posterior shape parameters given by Equations~\ref{eq:alpha} and~\ref{eq:beta} and $\mu_i$ is the known probability of force closure evaluated by exhaustive Monte-Carlo integration for a set of $M$ grasps.
We optimize this objective using Stochastic Gradient Descent (SGD) with the weights all initialized to 100.

### 2015-08-26 ICRA2016/bandits_docs/includes/experiments.tex
Created new figures and updated the full draft. Things are pretty rough but starting to come together. Still need to add new experiments, add a full algorithm section, clarify the use of priors, fill out neural net discussion, and generally clean thigns up. We are already beyond the acceptable length.

\section{Introduction}
\seclabel{extended-abstract}

Robots in warehouse order fullfillment and small- to medium-scale manufacturing must be able to efficiently grasp and manipulate new products and parts.
For example, a robot processing orders in a distribution warehouse must quickly plan graps for new consumer products to place them in shipping containers. 
% Above motivates speed and adaptivity
% Statement motivating robustness to uncertainty
Furthermore, a robot may not fully observe the state of the workspace, such as the pose or frictional properties of consumer products, due to sensor imprecision and missing data resulting from occlusions.
This poses a challenge for grasp planning with either analytic methods~\cite{ferrari1992, ciocarlie2009} that require precise knowledge of contact locations and surface normals or data-driven approaches~\cite{bohg2014data} that attempt to build a statistical model of grasp success over the massive number of configurations of the environment.
%This motivates an approach to grasp planning that is fast, robust to uncertainty about the state of the robot and environment, and can adapt to new objects and perturbations in the envrionment.

Past work has attempted to overcome this by planning grasps analytically with high probability of force closure~\cite{kehoe2012toward, kim2012physically, laskey2015bandits, mahler2015gp, weisz2012pose}, or using data-driven methods to predict grasp success from human labels~\cite{balasubramanian2012physical, detry2013learning,  herzog2014learning, kappler2015leveraging, lenz2015deep, saxena2008robotic} or empirical successes on a physical robot~\cite{boularias2014efficient, brook2011collaborative, detry2011learning, kroemer2010combining, montesano2012active}.
Many works on grasp selection with probablity of force closure evaluate a set of candidate grasps using sampling and select the highest quality grasp either using brute force sampling~\cite{kehoe2012toward, kim2012physically, weisz2012pose}, iterative pruning~\cite{kehoe2012estimating}, or Multi-Armed Bandit (MAB) algorithms to adaptively sample more promising grasps~\cite{barto1998reinforcement,
lai1985asymptotically, laskey2015bandits, robbins1985some}.
However, MAB algorithms, the current fastest sampling method, still required approximately 10 samples per grasp to converge to a solution and needed to be re-run for every new object.

On the other hand, data-driven approaches have shown promise over analytic methods on physical robot trials~\cite{balasubramanian2012physical, herzog2014learning} possibly due to a reduction in modelling error.
The number of objects and grasps tested is typically on the order of tens to hundreds for physical robot trials and at most a few thousand objects and hundreds of thousands of grasps when using simulation or human labels~\cite{goldfeder2009columbia, lenz2015deep, kappler2015leveraging}.
In comparison, state-of-the-art learning results in image classification~\cite{deng2009imagenet, krizhevsky2012imagenet} and speech recognition~\cite{cieri2004fisher, hannun2014deepspeech} relied on datasets containing tens of millions of examples.
This raises the question: will maching learning for grasp planning under vast numbers of possible object poses, object shapes, environment configurations, etc., exhibit scaling effects similar to those observed in computer vision and speech recognition?
%may require orders of magnitude more data than in use currently.

%This motivated gradient-based methods based on approximations to the probabliity of force closure~\cite{mahler2015gp} and using Multi-Armed Bandit algorithms to adaptively sample more promising grasps~\cite{laskey2015bandits}, which reduced the number of samples until convregence by 10$\times$.
%However, the number of iterations was still prohibitively high for real-time execution and prior knowledge could not be utilized for new objects.

To make progress toward answering this question, we introduce the Dexterity Network (DexNet) 1.0, a dataset of tens of thousands of 3D mesh models and a system for building statistical models that predict grasp quality across the dataset.
DexNet is composed of laser-scanned 3D mesh models from the KIT object database~\cite{kasper2012kit}, the Amazon Picking Challenge objects, BigBIRD~\cite{singh2014bigbird}, and YCB ~\cite{calli2015benchmarking}, and synthetic 3D mesh models from 3DNet~\cite{wohlkinger20123dnet} and the SHREC 2014 large scale object retrieval challenge~\cite{li2015comparison}.
~\figref{dexnet-teaser} shows a subset of the objects in the dataset.
To measure similarity between objects, we form an object network based on Deep Convolutional Neural Networks (CNNs) trained to predict object categories from synthetic rendered images of each object~\cite{aubry2015understanding, li2015comparison}.
The DexNet system uses Google Compute Engine to launch up to 600 instances at a time for evaluating grasp quality on subsets of objects and takes approximately 9.5 hours to run 1,800 objects on 180 instances.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.085]{figures/dexnet_collage.jpg}
\caption{Sample of 3D mesh models from the DexNet dataset. The dataset consists of over 30,000 models from laser-scanned datsets such as the KIT object database~\cite{kasper2012kit} and the Yale-CMU-Berkeley object set~\cite{calli2015benchmarking}, and synthetic datasets such as 3DNet\cite{wohlkinger20123dnet} and the SHREC 2014 object retrieval challenge dataset~\cite{li2015comparison} }
\figlabel{dexnet-teaser}
\vspace*{-15pt}
\end{figure}

In this work, we use DexNet to study the number of samples that MAB algorithms take to converge to a grasp with high probability of force closure across orders of magnitude of prior data of grasps with known quality.
To do so, we extend the MAB framework of Laskey et al.~\cite{laskey2015bandits} to model correlations between the probability of force closure for grasps on similar objects using Continuous Correlated Beta Processes (CCBPs)~\cite{goetschalckx2011continuous, montesano2012active}.
CCBPs allow us to form a prior belief on the quality of candidate grasps for a new object based on data in DexNet and to efficiently update a global belief on the quality of all candidate grasps on an object after observing the outcome of a single sampled grasp.
We measure local similarities between grasps on the same object by a distance between the gripper poses and the similarity between local surface patches near the mean location of contact on the object~\cite{herzog2014learning, kappler2015leveraging}.
We measure global similarity in shape based on the distance between the objects in DexNet.
While we acknowledge probability of force closure has shortcomings~\cite{balasubramanian2012physical}, we use it in this work because it is relatively inexpensive to evaluate computationally, allowing us to better examine the effects of scale.

\section{Preliminary Results}
\seclabel{prelim-experiments}
Preliminary experiments suggest that using CCBPs with prior data from DexNet reduces the number of samples for MAB algorithms to converge to a grasp with high probablity of force closure $P_F$ under uncertainty in object pose, gripper pose, and friction coefficient.
~\figref{local-mab} shows the normalized $P_F$ (the ratio of the $P_F$ for the sampled grasp to the $P_F$ in the candidate grasp set) versus iteration averaged over 20 trials for a cereal box and flower pot.
The plot compares Thompson sampling, a MAB algorithm, without correlations to Thompson sampling using the CCBP model of local grasp similiarity (no prior data).
We see that the CCBP model outperforms the uncorrelated model by approximately 10$\times$ for the cereal box but has comparable performance to Thompson sampling on the flower pot.
Iniitial reuslts suggest that performance on the flower pot is poorer because it has very few similar grasps according to our similarity metric.

@@

To examine the effects of orders of magnitude of prior data in the MAB algorithms, we first examined the effect of using prior data on smaller local datasets of 27 objects.
\figref{global-mab} shows the normalized probability of force closure $P_F$ versus iteration when planning grasps for the () using prior grasp data from the five nearest neighbor objects in DexNet out of 27 total objects averaged over 50 trials.
Each other object was labelled with 250 grasps and $P_F$ evaluated using brute force Monte-Carlo integration.
We see that running correlated MAB algorithms with even a small dataset of prior data (blue line) can significantly accelerate the convergence of MAB algorithms to a grasp with high $P_F$, even on an object for which correlated Thompson sampling without priors does not outperform uncorrelated Thompson sampling.
This suggests that adding more prior data may further accelerate convergence, because it is increasingly likely that a similar object and grasp exists in the dataset as the size increases.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.09]{figures/bottle_avg_reward_w_model.jpg}
\caption{Comparison of the normalized $P_F$ of the sampled grasp (y-axis) versus iteration of the MAB algorithm (x-axis) for correlated Thompson sampling with and without the use of prior grasps from five nearest neighbors from DexNet, uncorrelated Thompson sampling, and Uniform Allocation averaged over 20 trials on the bottle object. We see that convergence to within 90\% of the optimal grasp is accelerated by approximately 20$\times$, even with a small database of only 27 prior objects. }
\figlabel{global-mab}
\vspace*{-15pt}
\end{figure}

We are currently working on an experiment to quantify the gains in convergence time across orders of magnitudes of prior data (10, 100, 1000, 10000) from DexNet using Google Compute Engine.
Our initial version will be run on a relatively small subset of test objects, and in the coming weeks we will average the performance over a larger set of test objects.
We are particularly interested in seeing if there is a point of diminshing returns from adding more data when using datasets on the order of 10,000 - 100,000 objects.
We are also interested in whether or not adding perturbations to the data such as object reflections and shape perturbations will also increase performance, as has been observed for training Deep CNNs in vision~\cite{krizhevsky2012imagenet}.

>>>>

\section{Experiments}
\seclabel{experiments}

\subsection{Dataset}
To study the convergence rate with orders of magnitude of previous grasp data we create a dataset of tens of thousands of 3D CAD models.
We aggregated data from the laser scanned datasets Amazon Picking Challenge~\cite{}, BigBIRD~\cite{}, KIT~\cite{}, and YCB~\cite{}, as well as the synthetic datasets 3DNet~\cite{wohlkinger20123dnet} and the SHREC 2014 large-scale retrieval dataset~\cite{}.
To preprocess the data for grasping we set the frame of reference for each object to the the principal components of the vertices of each mesh, set the object center-of-mass as the center of a bounding box around the reoriented vertices, removed unreferenced and invalid vertices, rescaled each synthetic mesh such that its smallest principal direction fit within a PR2 gripper, and converted the mesh to a signed distance field.
We reserved the YCB dataset as a test set, and used subsets of the remaining data to train hyperparameters and to seed the CCBPs for convergence experiments on the test dataset.

\subsection{System}
To handle the scale of the experiments, we developed a Cloud-based software library on top of Google Cloud services.
We used Google Cloud Storage (GCS) to store the mesh models and to sample and evaluate 250 grasps per object.
Each model is stored in .OBJ format and the average size is roughly 0.5MB.
We used Google Compute Engine to distribute trials of MAB algorithms across objects, reducing the runtime of our large-scale experiments.
Our master analysis script can launch up to 600 GCE single core instances, each running Ubuntu 12.04.
When an instance is launched, we mount DexNet via a persistent disk containing a particular set of objects and grasps.
Each instance pulls our latest code from Github, runs a single python experiment script configured in a YAML file, compresses the results in an output directory, and uploads the results to GCS.
After all instances complete, the master script turns off all instances, unmounts all disks, downloads the results from each instance, and sends the user a notification email.
The results can be optionally analyzed by the master script.

\subsection{Rate of Convergence}
\TODO{Replace with final versions. The current results are preliminary}

Preliminary experiments suggest that using CCBPs with prior data from DexNet reduces the number of samples for MAB algorithms to converge to a grasp with high probablity of force closure $P_F$ under uncertainty in object pose, gripper pose, and friction coefficient.
~\figref{local-mab} shows the normalized $P_F$ (the ratio of the $P_F$ for the sampled grasp to the $P_F$ in the candidate grasp set) versus iteration averaged over 20 trials for a cereal box and flower pot.
The plot compares Thompson sampling, a MAB algorithm, without correlations to Thompson sampling using the CCBP model of local grasp similiarity (no prior data).
We see that the CCBP model outperforms the uncorrelated model by approximately 10$\times$ for the cereal box but has comparable performance to Thompson sampling on the flower pot.
Iniitial reuslts suggest that performance on the flower pot is poorer because it has very few similar grasps according to our similarity metric.

@@

To examine the effects of orders of magnitude of prior data in the MAB algorithms, we ran the algorithms with priors computed from increasingly larger subsets of prior data from DexNet: 0, 15, 150, and 1500 objects. 
\figref{global-mab} shows the normalized probability of force closure $P_F$ versus iteration when planning grasps for a bottle using prior grasp data from the five nearest neighbor objects in DexNet averaged over 50 trials.
Each other object was labelled with 250 grasps and $P_F$ evaluated using brute force Monte-Carlo integration.
We see that the convergence of the correlated MAB algorithms to a grasp with high $P_F$ accelerates with increasingly largers subsets of prior data used.
This suggests that adding more prior data may further accelerate convergence, because it is increasingly likely that a similar object and grasp exists in the dataset as the size increases.
Future work will examine these effects on a larger subset of objects and will use more than five nearest neighbors from DexNet to compute priors, which may lead to even larger gains for larger subsets of prior data.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.09]{figures/bottle_avg_reward_w_model2.jpg}
\caption{Comparison of the normalized $P_F$ of the sampled grasp (y-axis) versus iteration of the MAB algorithm (x-axis) for correlated Thompson sampling with and without the use of prior grasps from five nearest neighbors from DexNet, uncorrelated Thompson sampling, and Uniform Allocation averaged over 20 trials on the bottle object. Prior grasps were taken from increasingly larger subsets of DexNet: 15, 150, and 1500 objects. We see that convergence to within 90\% of the optimal grasp is accelerated by approximately 10$\times$ over uncorrelated Thompson sampling, and performance appears to improve with increasing sizes of the prior dataset used. }
\figlabel{global-mab}
\vspace*{-15pt}
\end{figure}

\TODO{Remove below section}
We are currently working on an experiment to quantify the gains in convergence time across orders of magnitudes of prior data (10, 100, 1000, 10000) from DexNet using Google Compute Engine.
Our initial version will be run on a relatively small subset of test objects, and in the coming weeks we will average the performance over a larger set of test objects.
We are particularly interested in seeing if there is a point of diminshing returns from adding more data when using datasets on the order of 10,000 - 100,000 objects.
We are also interested in whether or not adding perturbations to the data such as object reflections and shape perturbations will also increase performance, as has been observed for training Deep CNNs in vision~\cite{krizhevsky2012imagenet}.

\section{Sensitivity to Uncertainty}

### 2015-08-26 ICRA2016/bandits_docs/includes/extended_abstract.tex
Created new figures and updated the full draft. Things are pretty rough but starting to come together. Still need to add new experiments, add a full algorithm section, clarify the use of priors, fill out neural net discussion, and generally clean thigns up. We are already beyond the acceptable length.

To examine the effects of orders of magnitude of prior data in the MAB algorithms, we first examined the effect of using prior data on smaller local datasets of 27 objects.
\figref{global-mab} shows the normalized probability of force closure $P_F$ versus iteration when planning grasps for the () using prior grasp data from the five nearest neighbor objects in DexNet out of 27 total objects averaged over 50 trials.
Each other object was labelled with 250 grasps and $P_F$ evaluated using brute force Monte-Carlo integration.
We see that running correlated MAB algorithms with even a small dataset of prior data (blue line) can significantly accelerate the convergence of MAB algorithms to a grasp with high $P_F$, even on an object for which correlated Thompson sampling without priors does not outperform uncorrelated Thompson sampling.
This suggests that adding more prior data may further accelerate convergence, because it is increasingly likely that a similar object and grasp exists in the dataset as the size increases.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.09]{figures/bottle_avg_reward_w_model.jpg}
\caption{Comparison of the normalized $P_F$ of the sampled grasp (y-axis) versus iteration of the MAB algorithm (x-axis) for correlated Thompson sampling with and without the use of prior grasps from five nearest neighbors from DexNet, uncorrelated Thompson sampling, and Uniform Allocation averaged over 20 trials on the bottle object. We see that convergence to within 90\% of the optimal grasp is accelerated by approximately 20$\times$, even with a small database of only 27 prior objects. }
\figlabel{global-mab}
\vspace*{-15pt}
\end{figure}

>>>>

To examine the effects of orders of magnitude of prior data in the MAB algorithms, we ran the algorithms with priors computed from increasingly larger subsets of prior data from DexNet: 0, 15, 150, and 1500 objects. 
\figref{global-mab} shows the normalized probability of force closure $P_F$ versus iteration when planning grasps for a bottle using prior grasp data from the five nearest neighbor objects in DexNet averaged over 50 trials.
Each other object was labelled with 250 grasps and $P_F$ evaluated using brute force Monte-Carlo integration.
We see that the convergence of the correlated MAB algorithms to a grasp with high $P_F$ accelerates with increasingly largers subsets of prior data used.
This suggests that adding more prior data may further accelerate convergence, because it is increasingly likely that a similar object and grasp exists in the dataset as the size increases.
Future work will examine these effects on a larger subset of objects and will use more than five nearest neighbors from DexNet to compute priors, which may lead to even larger gains for larger subsets of prior data.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.09]{figures/bottle_avg_reward_w_model2.jpg}
\caption{Comparison of the normalized $P_F$ of the sampled grasp (y-axis) versus iteration of the MAB algorithm (x-axis) for correlated Thompson sampling with and without the use of prior grasps from five nearest neighbors from DexNet, uncorrelated Thompson sampling, and Uniform Allocation averaged over 20 trials on the bottle object. Prior grasps were taken from increasingly larger subsets of DexNet: 15, 150, and 1500 objects. We see that convergence to within 90\% of the optimal grasp is accelerated by approximately 10$\times$ over uncorrelated Thompson sampling, and performance appears to improve with increasing sizes of the prior dataset used. }
\figlabel{global-mab}
\vspace*{-15pt}
\end{figure}
